Cultural transmission models in python using simu\-P\-O\-P, Sci\-Py, and Num\-Py. Data storage is currently in a Mongo\-D\-B instance, which can be local or remote, if simulations are being run on multiple machines.

C\-T\-Py is a software layer on top of simu\-P\-O\-P by Bo Peng, currently version 1.\-X. See \href{http://simupop.sourceforge.net/}{\tt http\-://simupop.\-sourceforge.\-net/} for source code, license, and documentation.

\subsection*{Directory Structure}

analytics \-: python scripts which process simulation data from the database, and make entries into the database of their results.

ctpy \-: python modules and classes used in simulations and analytics

simulations \-: python scripts which run simu\-P\-O\-P simulations of cultural transmission models, logging samples to the database.

test \-: unit and functional test scripts

\subsection*{Runtime Dependency}

C\-T\-Py assumes that there is an instance of Mongo\-D\-B to which it can log samples and statistical data. The init.\-py file in the ctpy/sampling directory contains the database initialization, so that remote connections can be substituted for a local development server. This may be more easily configurable in future releases.

C\-T\-Py uses the \href{http://merciless.sourceforge.net/index.html}{\tt Ming} object relational library to connect from Python to Mongo\-D\-B.

\subsection*{Module Dependencies}

find . -\/name \char`\"{}$\ast$.\-py\char`\"{} $|$ xargs grep -\/h 'import ' $|$ grep -\/v ctpy $|$ grep -\/v simu $|$ sort $|$ cut -\/d' ' -\/f2 $|$ uniq $>$ required-\/modules.\-txt

\subsection*{Author}

Mark E. Madsen Copyright 2012-\/2013. All rights reserved. This software is made available under the Apache Software License (see file L\-I\-C\-E\-N\-S\-E), which allows you to use the software for commercial or non-\/commercial purposes, but you must attribute authorship, and derivatives must allow the user to find the original code and license.

\href{mailto:mark@madsenlab.org}{\tt mark@madsenlab.\-org} \href{http://notebook.madsenlab.org}{\tt Website and Lab Notebook} 